My First knitr Document

=======================

Download and read:

```{r Download and Read file}
if(!file.exists("./data")){dir.create("./data")}
fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(fileUrl, destfile = "./data/fitbit.zip", method = "curl")
unzip("./data/fitbit.zip", list = FALSE, overwrite = TRUE,
      junkpaths = FALSE, exdir = "./data", unzip = "internal",
      setTimes = FALSE)

fitbit <- read.csv("./data/activity.csv", sep = ",", header = TRUE)
```

Create a histogram:

```{r Histogram}

graph <- tapply(fitbit$steps,fitbit$date,sum)

hist(graph, breaks = 10, xlab = "Steps taken per day", main = paste("Histogram of Steps"))

```

Mean steps taken and Median:

```{r Mean Steps}
meansteps <- mean(graph, na.rm=TRUE)
mediansteps <- median(graph, na.rm=TRUE)
```

The mean is `r meansteps`. 
The median is `r mediansteps`.


Create a time series plot with interval and average steps.

```{r Time Series Plot}
routine <- tapply(fitbit$steps,fitbit$interval, mean, na.rm=TRUE)
intervaltime <- names(tapply(fitbit$steps,fitbit$interval, mean, na.rm=TRUE))
plot(routine~intervaltime, type = "l", xlab="Interval", ylab="Average Steps", col = "red", main = paste("Daily Routine"))
```

```{r MAX step interval}
max(routine)
```

This corresponds with interval 835-840!

Number of NA values:

```{r NA Values}
sum(is.na(fitbit$steps))
```

Strategy for filling missing data = mean for that 5 minute interval.

```{r Filling in NAs}
fitbit$steps[is.na(fitbit$steps)] <- with(fitbit, ave(steps, interval, 
   FUN = function(x) mean(x, na.rm = TRUE)))[is.na(fitbit$steps)]

```

Create a new dataset with the new estimates.

```{r New Dataset}
newdata <- fitbit
head(newdata)
```

Draw a new histogram with the new data set!

```{r New Histogram}
newgram <- tapply(newdata$steps,newdata$date,sum)

hist(newgram, breaks = 10, xlab = "Steps taken per day", main = paste("Histogram of Steps"))

```

Recalculate mean and median with new data set.

```{r New Mean and Median}

newmeansteps <- mean(newgram, na.rm=TRUE)
newmediansteps <- median(newgram, na.rm=TRUE)

```

The new mean is `r newmeansteps`. 
The new median is `r newmediansteps`.

These values are very similar to before. 
NA values do not affect much.
